Program Transformations for miniKanren

### 2020-05-21 papers/miniKanren/text/intro.tex
about transformers disagv

>>>>

While the aim of all meta-computation techniques is residual program efficiency, they rarely consider the residual program efficiency from the target language evaluator point of view.
The main optimization source is precomputing all possible intermediate and statically-known semantics steps at transformation-time while other criteria like residual program size or possible optimizations and execution cost of different language constructions by target language evaluator are usually out of consideration~\cite{jonesbook}.
It is known that supercompilation may adversely affect GHC optimizations yielding standalone compilation more powerful~\cite{SCBE,TCES} and cause code explosion~\cite{SCHC}.
Moreover, caused by transformer complexity it may be hard to predict real program speedup in each case on a bunch of examples even disregarding problems above.
Wherein, for example, for partial evaluation, an apogee of useless is the use of all static variables in a dynamic context only while it is known to be usefull for some specific form of language processors~\cite{jonesbook,bulyonkov84}.
Anyway, the formalization problem of cases for useful transformers application is poorly studied.
